Astr 513: Final Project

### 2016-05-09 Final_Project/ms.tex
Responded to EW's comment. Fixed a sentence about priors.

\subsection{Likelihood}
\label{sec:likelihood}
Using the above model for the distance modulus allows us to write a
probability that a model can generate our data:
%
\begin{align}
  \label{eq:likelihood}
  P(\mu(z)|\mathrm{cosmo}) &= \frac{1}{\sqrt{2\pi|\mathbf{C}|}}\nonumber \\
  &\qquad{}\exp\left[-\frac{1}{2} \sum_{i,j=0}^{N_{samples}}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_i 
    \mathbf{C}^{-1}_{i,j}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_j\right]
\end{align}
%
where $\mathbf{C}$ is the full covariance matrix between all of the $N_{samples}$ 
in the data, and $\mathrm{cosmo}$ represents the cosmology that we are investigating
(e.g. flat $\Lambda$CDM, $w$CDM, etc.). 
This is not the full picture though, since we must employ
Bayes' Theorum in order to include any priors on our choice of 
parameters and recover the posterior distribution function of our
parameters given our data
%
\begin{equation}
  \label{eq:posterior}
  P(\mathrm{cosmo}|\mu(z)) = P_{prior}(\mathrm{cosmo}) P(\mu(z)|\mathrm{cosmo}).
\end{equation}
%
\EW{Is this equation missing the normalization constant?}
For this work we investigate a combination of priors. \CosmoSIS is implemented
in a way that requires the user to provide bounds on the parameter space, which we
detail for each parameter in \autoref{tab:priors}.
Within those bounds, we investigated using a flat prior $P_{prior}=1$ and
\Planck priors.
\EW{This last sentence is confusing to me...}

>>>>

\subsection{Likelihood}
\label{sec:likelihood}
Using the above model for the distance modulus allows us to write a
probability that a model can generate our data:
%
\begin{align}
  \label{eq:likelihood}
  P(\mu(z)|\mathrm{cosmo}) &= \frac{1}{\sqrt{2\pi|\mathbf{C}|}}\nonumber \\
  &\qquad{}\exp\left[-\frac{1}{2} \sum_{i,j=0}^{N_{samples}}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_i 
    \mathbf{C}^{-1}_{i,j}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_j\right]
\end{align}
%
where $\mathbf{C}$ is the full covariance matrix between all of the $N_{samples}$ 
in the data, and $\mathrm{cosmo}$ represents the cosmology that we are investigating
(e.g. flat $\Lambda$CDM, $w$CDM, etc.). 
This is not the full picture though, since we must employ
Bayes' Theorum in order to include any priors on our choice of 
parameters and recover the posterior distribution function of our
parameters given our data
%
\begin{equation}
  \label{eq:posterior}
  P(\mathrm{cosmo}|\mu(z)) = P_{prior}(\mathrm{cosmo}) P(\mu(z)|\mathrm{cosmo}).
\end{equation}
%
\EW{Is this equation missing the normalization constant?}
\TM{No it is general. The equation before is normalized properly, and this one 
  doesn't specify the prior, so it is normalized in that the prior hasn't been
  specified yet.}
For this work we investigate a combination of priors. \CosmoSIS is implemented
in a way that requires the user to provide bounds on the parameter space, which we
detail for each parameter in \autoref{tab:priors}.
Within those bounds, we investigated differences between using flat prior $P_{prior}=1$ on
all parameters simultaneous in addition to \Planck priors on all parameters.
